\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-11 WOOT/Files/countermeasure.tex
Add limitation

\textbf{Distrust-by-Default.}
Most security issues of USB protocol is due to its \textit{trust-by-default} policy. \tool also relies on this feature to work. Hence if we reject all \textit{unauthorized} device, \tool and other many USB attacks will fail. It is worth mentioning here that \textit{distrust-by-default} policy is not the same as GoodUSB\cite{tian2015defending}. The GoodUSB relies on the \textit{unauthorized} device to complete its own authorization, while in this strict policy, users have to use an \textit{authorized} device. Though \textit{distrust-by-default} policy effectively prevents these attack, this also causes considerable inconvenience for users. For example, when there is no other \textit{authorized} device plugged, it is impossible for user to complete the authorization in the first place. Thus this strict policy is far from optimal in most use cases.

>>>>

\textbf{Distrust-by-Default.}
Most security issues of USB protocol is due to its \textit{trust-by-default} policy. \tool also relies on this feature to work. Hence if we reject all \textit{unauthorized} device, \tool and other many USB attacks will fail. It is worth mentioning here that \textit{distrust-by-default} policy is not the same as GoodUSB\cite{tian2015defending}. GoodUSB relies on the \textit{unauthorized} device to complete its own authorization, while in this strict policy, users have to use an \textit{authorized} device. Though \textit{distrust-by-default} policy effectively prevents these attack, this also causes considerable inconvenience for users. For example, when there is no other \textit{authorized} device plugged, it is impossible for user to complete the authorization in the first place. Thus this strict policy is far from optimal in most use cases.

### 2021-01-11 WOOT/Files/discussion.tex
Update comments
Update countermeasures
Add limitation

\section{Discussion}
\label{sec:discussion}
\outline{Defenses}

>>>>

\section{Discussion}
\label{sec:discussion}

\subsection{Limitation}
There exist multiple limitations of \tool.
To begin with, \tool can only gain the information and control access of the host itself instead of external hardware.
Consequently, as we introduced in the Section\ref{sec:countermeasures}, \tool can hardly bypass the defence approaches which use external hardware for authorization.
Moreover, most of the devices will prompt users to give authentication to the USB devices or select one of the functional modes after they are plugged in.
Though some of such prompts are not conspicuous for non-experts, especially when \tool is concealed within other functional hardware such as portable battery \shuqing{If there is experiment, add it here.}, the probability whether users could get aware that something unusual happens will increase with the existence these prompting messages.

\subsection{Impact}
